wgcna

### 2019-08-23 analysis/08_wgcna.Rmd
smaller font

```{r wgcna-male, message=FALSE, warning=FALSE, cache=TRUE}
source("08_WGCNA_1_params.R")
subsetWGCNA(c("male.gonad", "male.hypothalamus", "male.pituitary"))
```

@@

```{r wgcna-hyp, message=FALSE, warning=FALSE, cache=TRUE}
source("08_WGCNA_1_params.R")
subsetWGCNA(c("male.hypothalamus", "female.hypothalamus"))
```

@@

```{r wgcna-gon, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("female.gonad", "male.gonad"))
```

>>>>

```{r wgcna-male, message=FALSE, warning=FALSE, cache=TRUE}
source("08_WGCNA_1_params.R")
subsetWGCNA(c("male.gonad", "male.hypothalamus", "male.pituitary"))

@@

```{r wgcna-hyp, message=FALSE, warning=FALSE, cache=TRUE}
source("08_WGCNA_1_params.R")
subsetWGCNA(c("male.hypothalamus", "female.hypothalamus"))

@@

```{r wgcna-gon, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("female.gonad", "male.gonad"))
